Hello OpenScPCA

### 2024-03-15 analyses/hello-R/notebooks/hello.Rmd
More responses to review

We will be creating two output files: a table and a plot.
Defining their locations here will make it easy for later users to know what to expect.

@@

Finally, we will plot the results as a histogram, faceted and colored by project ID.

@@

Now let's save the plot.
```{r}
ggsave(count_plot, plot_file, width = 8, height = 6)
```

>>>>

We will be creating two output files: a table and a plot.
Defining their locations in the `Setup` section will make it easy for future notebook users to know what to expect.

@@

Finally, we will plot the results as a faceted histogram, colored by project ID.

@@

Now let's save the plot.

```{r}
ggsave(plot_file, count_plot, width = 8, height = 6)
```
